\renewcommand{\baselinestretch}{1.5} %設定行距
\pagenumbering{roman} %設定頁數為羅馬數字
\clearpage  %設定頁數開始編譯
\sectionef
\addcontentsline{toc}{chapter}{摘~~~要} %將摘要加入目錄
\begin{center}
\LARGE\textbf{摘~~要}\\
\end{center}
\begin{flushleft}
\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 機械設計在許多實體產品開發流程中一直扮演著重要角色. 然而隨著設計的複雜性與對精確模擬的需求的增加, 電腦輔助設計 (Conputer Aided Design, CAD) 與有限元素分析 (Finite Element Analysis, FEA) 套件已經成為機械設計流程中不可或缺的工具. 而在這些工具中, 目前位於 Siemens 公司旗下的 Solid Edge 與 Femap 因其具有完整的機械設計相關模組, 以及友善的應用程式界面而受到歡迎。\\[12pt]
\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 本專題旨在探討 Solid Edge 與 Femap 在機械設計中的應用. 其中將使用 Solid Edge 以及 Femap 中提供的模擬和分析技術應用在所選擇的產品設計過程. 此外, 本專題還將介紹使用 Solid Edge 創建並使用 Femap 進行分析的機械設計案例研究。\\[12pt]
\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 本專題報告首先將對機械設計中有關 Solid Edge 和 Femap 的相關文獻進行回顧. 其中將包括對相關理論和概念的討論. 本報告也將介紹 Solid Edge 工程參考 (Engineering Reference) 模組中, 對於各類機械元件設計與自動繪圖的使用方法。\\[12pt]
\fontsize{14pt}{20pt}\sectionef\hspace{12pt}\quad 案例研究部分將展示使用 Solid Edge 創建並使用 Femap 進行分析的機械設計的相關範例.  結果和討論部分則將根據案例研究分析 Solid Edge 和 Femap 在機械設計中與使用其他類似套件的方便性與優勢. 最後, 結論部分將總結專題報告結果並為未來的工作提出建議。\\[12pt]

\end{flushleft}
\begin{center}
\fontsize{14pt}{20pt}\selectfont 關鍵字: solid edge、femap 、有限元素分析、同步建模
\end{center}
\newpage
%=--------------------Abstract----------------------=%
\renewcommand{\baselinestretch}{1.5} %設定行距
\addcontentsline{toc}{chapter}{Abstract} %將摘要加入目錄
\begin{center}
\LARGE\textbf\sectionef{Abstract}\\
\begin{flushleft}
\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad Mechanical design has always played an important role in many physical product development processes. However, with the increase in design complexity and the need for accurate simulation, Computer Aided Design (Computer Aided Design, CAD) and Finite Element Analysis (Finite Element Analysis, FEA) package has become an indispensable tool in the mechanical design process. Among these tools, Solid Edge and Femap, which are currently under Siemens, are well received for their complete mechanical design-related modules and friendly Application Programming Interfaces (API).   \\[12pt]
\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad This project aims to explore the application of Solid Edge and Femap in mechanical design. It will use Solid Edge and the simulation and analysis technology provided in Femap to apply to the selected product design process. In addition, this project will also introduce the use of Solid Edge to create A mechanical design case study analyzed with Femap. \\[12pt]
\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad This special report will first review the relevant literature on Solid Edge and Femap in mechanical design. It will include a discussion of related theories and concepts. This report will also introduce Solid Edge Engineering Reference module, which can be applied to specific mechanical elements design as well as for automatic creation of the associated parts and assemblies.\\[12pt]
\fontsize{14pt}{16pt}\sectionef\hspace{12pt}\quad The Case Study section will present relevant examples of mechanical design created with Solid Edge and analyzed with Femap. The Results and Discussion section will analyze the convenience and advantages of using Solid Edge and Femap in mechanical design with other similar packages based on the case study. Finally, the concluding section will summarize the findings and make recommendations for future work.\\[12pt]
\end{flushleft}
\begin{center}
\fontsize{14pt}{16pt}\selectfont\sectionef Keyword:   solid edge、femap、Finite element method
\end{center}
